Macroscopic Salt Rejection through Electrostatically Gated Porous Graphene

### 2019-01-10 paper/paper.tex
Fix PG+PTCE name in paper

We next discuss the effects of electrostatic gating on graphene. In
order to avoid any interference from the conductivity probe to the
membrane potential, the “three-interval” method, which has been used
in controlling the membrane potential in mesoporous carbon membranes
\cite{Surwade_2014}, is adopted here. \Fig{} \ref{fig:2}a
illustratively represents how the measured conductivity evolves with
time. Specifically, in the first interval, the gate voltage source is
turned off and the conductivity probe is on, allowing us to obtain the
conductivity-time profile with an average slope $s_{1}$ that
corresponds to the diffusive flux across the PG-PCTE membrane. In the
second interval, a voltage $V_{\mathrm{G}}$ is applied to the membrane
after turning off the conductivity probe, followed by the third
interval $s_{3}$, in which the conductivity probe is turned on again
to give the corresponding slope. A control experiment was performed to
ensure the copper tape was not in direct contact with the ionic
solution (Supplementary Section \ref{SI-sec:copper}). The slope corresponding to the
second interval $s_{2}$, as the conductivity probe is off, is
determined by linear interpolation of the conductivities from the
endpoint of interval 1 to the starting point of interval 3. A decrease
of slope observed in interval 2 indicates that the total flux through
PCTE+PG is reduced upon gating (i.e. salt penetration through the PG
pores is partially rejected). We define such experimentally measured
reduction rate as $\eta$, which is equivalent to the decrease of total
diffusive flux through PCTE+PG as follows:
\begin{equation}
  \label{eq:rejection}
  \eta = \frac{\bar{s} - s_{2}}{\bar{s}} = \frac{\boldsymbol{J}_{\mathrm{PG0}}
    - \boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})}{\boldsymbol{J}_{\mathrm{PG0}}}
\end{equation}
where $\bar{s}$ is the average slope of $s_{1}$ and $s_{3}$, namely
$(s_{1} + s_{3})/2$, and
$\boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})$ is the diffusive flux
across the PTCE-supported PG double layer as a function of
$V_{\mathrm{G}}$. PG and PCTE membranes effectively form a transport
system with series resistance $R_{\mathrm{PG}}$ (tunable by
$V_{\mathrm{G}}$) and $R_{\mathrm{PCTE}}$ (independent of
$V_{\mathrm{G}}$), respectively. Due to the dominance of
$R_{\mathrm{PCTE}}$ in the ionic transport, significant reduction of
total ionic flux can only be achieved, when
$R_{\mathrm{\mathrm{G}}}(V_{\mathrm{G}} \neq 0) \gg
R_{\mathrm{\mathrm{G}}}^{0}$. Using the circuit analog model, we can
extract the effective salt rejection ratio of PG $\xi$ from the
observable flux reduction ratio $\eta$, as a function of
$V_{\mathrm{G}}$ as (details see Supplementary Section
\ref{SI-sec:R-model}):
\begin{equation}
\label{eq:xi-def}
\xi = \frac{(\delta+1) \eta}{\delta \eta + 1}
\end{equation}
The factor $\xi$ enables a reliable and stable measurement of salt
rejection through the PG membrane, as the salt species and initial
conditions may induce a degree of measurement uncertainty between
different samples.

>>>>

We next discuss the effects of electrostatic gating on graphene. In
order to avoid any interference from the conductivity probe to the
membrane potential, the “three-interval” method, which has been used
in controlling the membrane potential in mesoporous carbon membranes
\cite{Surwade_2014}, is adopted here. \Fig{} \ref{fig:2}a
illustratively represents how the measured conductivity evolves with
time. Specifically, in the first interval, the gate voltage source is
turned off and the conductivity probe is on, allowing us to obtain the
conductivity-time profile with an average slope $s_{1}$ that
corresponds to the diffusive flux across the PG-PCTE membrane. In the
second interval, a voltage $V_{\mathrm{G}}$ is applied to the membrane
after turning off the conductivity probe, followed by the third
interval $s_{3}$, in which the conductivity probe is turned on again
to give the corresponding slope. A control experiment was performed to
ensure the copper tape was not in direct contact with the ionic
solution (Supplementary Section \ref{SI-sec:copper}). The slope corresponding to the
second interval $s_{2}$, as the conductivity probe is off, is
determined by linear interpolation of the conductivities from the
endpoint of interval 1 to the starting point of interval 3. A decrease
of slope observed in interval 2 indicates that the total flux through
PG-PCTE is reduced upon gating (i.e. salt penetration through the PG
pores is partially rejected). We define such experimentally measured
reduction rate as $\eta$, which is equivalent to the decrease of total
diffusive flux through PG-PCTE as follows:
\begin{equation}
  \label{eq:rejection}
  \eta = \frac{\bar{s} - s_{2}}{\bar{s}} = \frac{\boldsymbol{J}_{\mathrm{PG0}}
    - \boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})}{\boldsymbol{J}_{\mathrm{PG0}}}
\end{equation}
where $\bar{s}$ is the average slope of $s_{1}$ and $s_{3}$, namely
$(s_{1} + s_{3})/2$, and
$\boldsymbol{J}_{\mathrm{PG}}(V_{\mathrm{G}})$ is the diffusive flux
across the PTCE-supported PG double layer as a function of
$V_{\mathrm{G}}$. PG and PCTE membranes effectively form a transport
system with series resistance $R_{\mathrm{PG}}$ (tunable by
$V_{\mathrm{G}}$) and $R_{\mathrm{PCTE}}$ (independent of
$V_{\mathrm{G}}$), respectively. Due to the dominance of
$R_{\mathrm{PCTE}}$ in the ionic transport, significant reduction of
total ionic flux can only be achieved, when
$R_{\mathrm{\mathrm{G}}}(V_{\mathrm{G}} \neq 0) \gg
R_{\mathrm{\mathrm{G}}}^{0}$. Using the circuit analog model, we can
extract the effective salt rejection ratio of PG $\xi$ from the
observable flux reduction ratio $\eta$, as a function of
$V_{\mathrm{G}}$ as (details see Supplementary Section
\ref{SI-sec:R-model}):
\begin{equation}
\label{eq:xi-def}
\xi = \frac{(\delta+1) \eta}{\delta \eta + 1}
\end{equation}
The factor $\xi$ enables a reliable and stable measurement of salt
rejection through the PG membrane, as the salt species and initial
conditions may induce a degree of measurement uncertainty between
different samples.
